Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-05-31 analysis/paper/shceof.Rmd
Borra mención de monopolo
Aclara frase del PSA

Figure \@ref(fig:phase-histogram) shows an histogram that counts the number of SON seasons in which the cEOF2 phase was close to each of the four particular phases (positive/negative of real/imaginary component), with the observations for each season marked as rugs on the horizontal axis.
In `r scales::percent(imaginary)` of seasons cEOF2 has a phase similar to either the negative or positive imaginary phase, making the imaginary phase the most common phase. 
This is also, by construction, the phase that is most correlated with ENSO.
Therefore, the Imaginary cEOF2 explains more variance than the Real cEOF2 and conventional EOF analysis will tend to separate the two.

@@

The cEOF1 represents the variability of the zonal wave 1 in the stratosphere, but represents a more zonally symmetric monopole in the troposphere.
There is a statistically positive trend in the magnitude of this cEOF, which is consistent with previous studies that showed secular changes in springtime wave-1-like patterns [e.g. @raphael2003].
This mode is closely related to stratospheric variability such as anomalies in Total Ozone Column.
Otherwise, this complex EOF is not related with SST variability and continental precipitation in the Southern Hemisphere.

>>>>

Figure \@ref(fig:phase-histogram) shows an histogram that counts the number of SON seasons in which the cEOF2 phase was close to each of the four particular phases (positive/negative of real/imaginary component), with the observations for each season marked as rugs on the horizontal axis.
In `r scales::percent(imaginary)` of seasons cEOF2 has a phase similar to either the negative or positive imaginary phase, making the imaginary phase the most common phase. 
This is also, by construction, the phase that is most correlated with ENSO.

Therefore, by virtue of being the most common phase, the Imaginary cEOF2 explains more variance than the Real cEOF2.
Conventional EOF analysis will therefore tend to separate them relatively cleanly, with the EOF representing the Imaginary cEOF2 always leading the one representing the Real cEOF2.

@@

The cEOF1 represents the variability of the zonal wave 1 in the stratosphere.
There is a statistically positive trend in the magnitude of this cEOF, which is consistent with previous studies that showed secular changes in springtime wave-1-like patterns [e.g. @raphael2003].
This mode is closely related to stratospheric variability such as anomalies in Total Ozone Column.
Otherwise, this complex EOF is not related with SST variability and continental precipitation in the Southern Hemisphere.
